\huge A Usability Evaluation of Tor Launcher

### 2017-02-15 pets2017-paper/pets2017-paper.tex
delete reference to extraneous information
shuffle some things around.

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked a prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to report their age, so age calculations omit this participant's information. All of our users were highly educated, having at least some college education. We show their self-reported familiarity with technical terms use of security tools in  Appendix~\ref{prescreening-responses}. We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.

@@

\subsection{Results} 
We use out screen recording and interview data to give a summary of each participant.

%TODO: re-watch the videos and get the exact times. 
%https://github.com/lindanlee/PETS2017-paper/tree/master/sessions/pre/videos

@@

@@

\section{Recommendations}
\label{sec:recommendations}
We believe that adopting our design will save users time. But since we did not test our design changes independently, we cannot (and do not) claim the effects each change. We do not recommend specific changes, but offer some suggestions based on what we learned: \\

@@

We also recommend exploring solutions that leverage automation, user-dependent inputs, or network-dependent inputs. We start this discussion by sharing some of our own ideas in appendix~\ref{alternatives}.

@@

@@

\section{Alternative Approaches} 
\label{alternatives}
We list some of our ideas:\\
\begin{description}
\item{\bfseries Suggest bridges based on country.} Give users information about which bridges would work in their country. one way to do this is to show a list of countries with a corresponding recommended configuration. This requires developers to maintain a list of suggestions and that the users trust the suggestions. 
\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publicly associated with Tor, using transport that obfuscates their connection. If users are not sensitive, let them configure their own bridges and proxies. 
\item{\bfseries Ask users if they know what to do.} If they know, offer the option to manually configure bridges and proxies. If they do not know, give suggestions on what to do next or automate the process for them somehow. This requires users to answer honestly to the question and to trust the suggestions given. 
\item{\bfseries Automate naively.} Have the interface automatically try configurations that would most likely work, in order (i.e. a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy). This is what most users would ideally do anyway. However, this method leaks to network eavesdroppers that the user is using Tor without the user's awareness. 
\item {\bfseries Automate naively after users fail.} Let users try to configure bridges and proxies. If they fail, then a network eavesdropper already knows that the user is trying to connect to Tor. We believe there is negligible added risk to naively automate the connection. 
\item{\bfseries Automate in a smart way.} The interface first detects proxy settings and uses them, if any. Then it automatically connects to some secret bridges that will always work, which assign the user an entry relay that works based on their location. This requires having an invincible set of high-bandwidth bridges that work for every single user around the world.  
\end{description}
We believe that these ideas can significantly help users connect to Tor.

>>>>

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked a prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to report their age, so age calculations omit this participant's information. All of our users were highly educated, having at least some college education. We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.

@@

\subsection{Results}

To see a summary of what each of our 16 participants did, see Appendix~\ref{summaries}.

@@

%\section{Alternative Approaches} 
%\item{\bfseries Suggest bridges based on country.} Give users information about which bridges would work in their country. one way to do this is to show a list of countries with a corresponding recommended configuration. This requires developers to maintain a list of suggestions and that the users trust the suggestions. 
%\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publicly associated with Tor, using transport that obfuscates their connection. If users are not sensitive, let them configure their own bridges and proxies. 
%\item{\bfseries Ask users if they know what to do.} If they know, offer the option to manually configure bridges and proxies. If they do not know, give suggestions on what to do next or automate the process for them somehow. This requires users to answer honestly to the question and to trust the suggestions given. 
%\item{\bfseries Automate naively.} Have the interface automatically try configurations that would most likely work, in order (i.e. a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy). This is what most users would ideally do anyway. However, this method leaks to network eavesdroppers that the user is using Tor without the user's awareness. 
%\item {\bfseries Automate naively after users fail.} Let users try to configure bridges and proxies. If they fail, then a network eavesdropper already knows that the user is trying to connect to Tor. We believe there is negligible added risk to naively automate the connection. 
%\item{\bfseries Automate in a smart way.} The interface first detects proxy settings and uses them, if any. Then it automatically connects to some secret bridges that will always work, which assign the user an entry relay that works based on their location. This requires having an invincible set of high-bandwidth bridges that work for every single user around the world.  
%\end{description}
%We believe that these ideas can significantly help users connect to Tor.

@@

\section{Recommendations}
\label{sec:recommendations}
We offer some suggestions based on what we learned: \\

@@

While we believe that adopting our design faithfully will save users time. But since we did not test our design changes independently, we cannot (and do not) claim the effects each change. Alternative designs may be better solutions.

@@

\section{Qualitative Testing Observations}
\label{summary}
We summarize of each participant's session.

% re-watched the videos and get the exact times. 
%https://github.com/lindanlee/PETS2017-paper/tree/master/sessions/pre/videos

@@
